Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-07 paper.tex
provide more definition of fleet and continuous

Another difference between fleet-based and individual facility modeling
involves fuel sharing.  Power production by a group of individual reactors for
a fixed amount of fuel shortage may vary depending on how available fuel is
distributed.  This is illustrated in Figure \ref{fig:fuel-sharing}.  A system
being short 3 batches might mean that one reactor has no batches and isn't
operating or that 3 reactors are each missing a single batch.  This is
referred to as the \emph{fuel sharing effect}.  Fleet reactors, by design,
have perfect fuel sharing - all fuel is distributed so that the minimum
possible amount of capacity is offline during shortages. The most correct
measure of fuel sharing inefficiency is the difference between the actual
generated power and the maximum amount of power that could have been generated
among all possible fuel distribution alternatives.  This is difficult to
actually compute. One possible approximation is to count the number of fresh
fuel batches distributed to reactors that ended up not having enough fuel to
operate (i.e. a full core) that time step.  This approximation assumes that
every "wasted" batch of fuel, could have been given to a reactor that only
needed one batch to operate.

>>>>

Another difference between fleet-based and individual facility modeling
involves fuel sharing.  Power production by a group of individual reactors for
a fixed amount of fuel shortage may vary depending on how available fuel is
distributed.  This is illustrated in Figure \ref{fig:fuel-sharing}.  A system
being short 3 batches might mean that one reactor has no batches and isn't
operating or that 3 reactors are each missing a single batch.  This is
referred to as the \emph{fuel sharing effect}.  Fleet reactors, by design,
have perfect fuel sharing - all fuel is distributed so that the minimum
possible amount of capacity is offline during shortages. The most correct
measure of fuel sharing inefficiency is the difference between the actual
generated power and the maximum amount of power that could have been generated
among all possible fuel distribution alternatives.  This is difficult to
actually compute. One possible approximation is to count the number of fresh
fuel batches distributed to reactors that ended up not having enough fuel to
operate (i.e. a full core) that time step.  This approximation assumes that
every "wasted" batch of fuel, could have been given to a reactor that only
needed one batch to operate.  Equation \ref{eq:badshare} describes such an
approximation.

\begin{equation}
    N_{wasted}(t) = \sum\limits_{r \in R_t} \left(H[t-S_{sched}(t,r)] \cdot [1-O(t,r)]  \sum\limits_{t'=F_{prev}(t,r)}^{t} N_b(t',r) \right)
    \label{eq:badshare}
\end{equation}

where $R_t$ is the set of all reactors, $H$ is the Heaviside function,
$S_{sched}(t,r)$ is the original scheduled startup time of reactor $r$ after
the most recent refueling outage that started before $t$, $F_{prev}(t,r)$ is
the start of the most recent refueling outage for reactor $r$ before or on
time $t$, $O(t,r)$ is 1 if reactor $r$ is producing power at time $t$ and zero
otherwise, and $N_b(t,r)$ is the number of new fuel batches received by
reactor $r$ since time $t$.
